Looking for CDI Bias

### 2021-07-01 01-preliminary.Rmd
Update 01-preliminary.Rmd
minor changes

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE)

library(wordbankr)
library(tidyverse)
library(ggrepel)
library(mirt) # requires package loading, not just referencing. 
library(mirtCAT)
library(here)
library(kableExtra)
library(gridExtra)
library(printr)
#library(parallel)
#library(doParallel)
#library(mclust)
#library(Rtsne)
#library(factoextra)
```

@@

>>>>

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE)
# new libraries GK
# new line
library(wordbankr)
library(tidyverse)
library(ggrepel)
library(mirt) # requires package loading, not just referencing. 
library(mirtCAT)
library(here)
library(kableExtra)
library(gridExtra)
library(printr)
#library(parallel)
#library(doParallel)
#library(mclust)
#library(Rtsne)
#library(factoextra)
```

@@

Test
